Getting mortality from atlantisom: backing out F and M from Z

### 2020-01-16 TestCalcFandM.Rmd
Z and M are killing me here

@@

@@

>>>>

# WARNING only works for CCA because YOY.txt rows 2:end are already in numbers
# and we are merging out the incorrect and irrelevant YOY row 1 (Time=0)
# also hardcoded for sardine example
recnums <- YOY_ss %>%
  mutate(yr = as.integer(round(YOY_ss$Time)/365)) %>%
  mutate(recnums = SSH.0/k_wetdry/biol$redfieldcn)

@@

plotZ <- ggplot() +
  geom_line(data=Zish, aes(x=Time/365, y=relZ, color="mort.txt Z")) +
  #geom_point(data=fullresZ, aes(x=time/stepperyr, y=atoutput, color="each timestep Z")) +
  geom_point(data=annZ1, aes(x=yr-1, y=Z, color="annual Z")) +
  geom_point(data=annZ2, aes(x=yr-1, y=Z, color="sum timestep Z")) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, species_ss))

@@

#what about annual Z from totnumss catch curve?
# each timestep use lm(agecl~ log(atoutput))
library(dplyr)
library(broom) # to change model results into data frame
catchcurve1 <- totnumss %>% 
  group_by(time) %>%
  do(tidy(lm(log(popnum) ~ agecl, data = .))) %>% 
  filter(term == "agecl")

# or do for the year averaging natage at each timestep?
catchcurve2 <- totnumss %>%
  mutate(yr = floor(time/stepperyr)+1) %>%
  group_by(yr, agecl) %>%
  summarise(avgpopnum = mean(popnum)) %>%
  do(tidy(lm(log(avgpopnum) ~ agecl, data = .))) %>% 
  filter(term == "agecl")

altZ1 <- catchcurve1 %>%
  select(time, estimate) %>%
  mutate(yr = floor(time/stepperyr)+1) %>%
  group_by(yr) %>%
  summarise(Z = sum(-estimate))

altZ2 <- catchcurve2 %>%
  mutate(Z=-estimate) %>%
  select(yr, Z)

#another alternative tracking cohorts
# get rid of agecl 1 to ignore recruitment
# still need rec_time to know when they go to next agecl
# survival is 
#  within year 
# SSH actually have two ages per agecl so this wont work
# also, when I look at an age class numbers are INCREASING each timestep
# which makes no sense unless there is migration in?
